Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-09-27 manuscript.Rmd
pilot is an alternative to simulation

>>>>

Another approach that can replace but also complement simulated data is to conduct a pilot study [@thabaneTutorialPilotStudies2010] and use the resulting data to preregister.
A pilot study has obvious advantages for study planning, since it lets researcher evaluate the feasibility of many assumptions.
However, we must warn our readers, while piloting is more traditional than our approach of obfuscating the data before preregistration it may not be innocuous to use the resulting data and care must be taken to avoid errors of sequential testing [@whiteheadBiasMaximumLikelihood1986].
